OECD TiVa LMIC GVCs

### 2015-04-21 OECD-TiVa-LMIC-GVCs.Rmd
add package description
adde xample graph

@@

>>>>

 ```{r}
 library(decompr)
 ls.str("package:decompr")
 ```

 ```{r}
 library(gvc)
 ls.str("package:gvc")
 ```

 ```{r, echo=FALSE}
 # load the data
load("data/gvc_indicators.RData")
load("data/nrca_df.RData")
load("data/country_vars.RData")
load("data/w1995_2008.RData")

 # load required libraries
library(dplyr)
library(ggvis)
library(magrittr)

# contruct avg_pop and gdp
country_vars %<>%
  group_by(ctry) %>%
  summarise(avg_pop = mean(pop)) %>%
  merge(country_vars, . , by = "ctry")

country_vars$avg_gdp <- with(country_vars, avg_pop * avg_gdppc)

# create factor gdp var
country_vars$ic      <- with(country_vars, ifelse(avg_gdppc <= 6000, "lic",
                                                  ifelse(avg_gdppc > 12000, "hic", "mic") ) )

# merge wwz and country vars
w1995_2008 %<>% merge(country_vars,
                      by.x = c("year", "Exporting_Country"),
                      by.y = c("year", "ctry")              )

# merge gvc indicators and country vars
gvc_indicators %<>% merge(country_vars, by = c("ctry", "year") )

# merge gvc indicators and nrca
gvc_indicators %<>% merge(nrca, by.x = c("ctry", "isic", "year"), by.y = c("country", "industry", "year") )
```

@@

 ```{r}
 gvc_indicators %>%
  group_by(year, ic) %>%
  summarise(i2e = sum(fvax_ams_ik) / sum(exports_ik) ) %>%
  ggvis(~year, ~i2e, stroke = ~ic ) %>%
  layer_lines()
 ```
